\documentclass[11pt]{article}
\usepackage{../EllioStyle}

\title{Homework 1}
\author{Elliott Pryor}
\date{31 Jan 2021}

\rhead{Homework 1}

\begin{document}
\maketitle

\problem{1} 6.2.4 Problem 6

Prove that if $f$ is Riemann integrable on $[a, b]$ and $g(x) = f(x)$ for
every $x$ except for a finite number, then $g$ is Riemann integrable.

\textbf{Hint:} Mimic the proof of Theorem 6.2.3

\hrule

\begin{proof}
    
    Let $a_1, a_2, ..., a_N$ denote the points where $g(a_i) \neq f(a_i)$.
    Given any $1/n$ surround each $a_k$ by an interval $I_k$ such that $|I_k| < 1/n$. Then,
    $g$ equals $f$ and is Riemann integrable on $[a,b]$ with $\cup_{k = 1} ^N I_k$ removed.

    Then, we estimate the contribution to the oscillation from the $I_k$ intervals. First, $f$ must be bounded since
    it is Riemann-integrable. Then since $g$ differs from $f$ at a finite number of locations, it must also be bounded. 
    Then let $M = \sup _{x \in [a,b]} g(x)$ and $M = \inf _{x \in [a,b]} g(x)$. Then the contribution of any of the intervals:
    $I_k$ is at most $1/n \cdot (M-m)$. There are $N$ such intervals, so the total contribution to oscillation is $N/n \cdot (M - m)$.

    Then for the remaining intervals: $[a,b] \setminus \cup_{k = 1} ^N I_k$, $g = f$. Since $f$ is Riemann-integrable,
    the oscillation on these intervals can be made sufficiently small by choosing the partition size sufficiently small. 
    In other words, the total oscillation on a partition $P'$ of $[a,b] \setminus \cup_{k = 1} ^N I_k$, $g = f$ can be,
    $\forall 1/n \sp \exists 1/m \sp st \sp Osc(g, P') < 1/n$ for $|P'| < 1/m$ (part b of Theorem 6.2.1)

    Then the total oscillation $Osc(g, P) < 1/n + N/n \cdot (M - m)$. Since $N, M, m$ are constant, there exists a sequence of 
    partitions such that $Osc(g, P_j) \to 0 \sp as \sp j \to \infty$ by selecting $n$ large enough.


\end{proof}



\problem{2} 6.2.4 Problem 9, part b

If $f$ is Riemann integrable on $[a, b]$, prove $F(x) = \int_a ^x f(t) dt$ satisfies a Lipschitz condition

\hrule


\begin{proof}
    We need to show that $|F(x) - F(x_0)| \leq M |x - x_0|$ for some $M$.

    Without loss of generality assume $x > x_0$. Then by the definition of $F$. 
    We have $$|F(x) - F(x_0)| = \int_a ^x f(t) dt - \int_a ^{x_0} f(t) dt = \int_{x_0} ^x f(t) dt$$ 
    We say $M = \sup_{x \in [a,b]} f(x)$. 
    Then since $f(t) \leq M \sp \forall t \in [a,b]$
     $$|F(x) - F(x_0)| = \int_{x_0} ^x f(t) dt \leq \int_{x_0} ^x M dt = M |x - x_0|$$ as required.
\end{proof}

\problem{3} 6.2.4 Problem 10

If $f$ is Riemann integrable on $[a, b]$ and continuous at $x_0$, prove
that $F(x) = \int_a ^x f(t) dt$ is differentiable at $x_0$ and $F'(x_0) = f(x_0)$.
Show that if $f$ has a jump discontinuity at $x_0$, then $F$ is not
differentiable at $x_0$. 

\textbf{Hint: } Refer to the proof of Theorem 6.1.2, note that $f(x)$ being continuous at $x_0$
can be written as $\forall 1/m, \sp \exists 1/n \sp st. \sp \forall x \in [a,b], \sp |x - x_0| < 1/n$, we have $|f(x) - f(x_0)| < 1/m$
or $f(x_0) - 1/m < f(x) < f(x_0) + 1/m$
\hrule


\begin{proof}
    
    We show this in two parts. We first show that if $f(x)$ is continuous at $x_0$ then $F'(x_0)$ exists and equals $f(x_0)$.
    So we want to show $\lim_{h \to 0} \frac{F(x_0 + h) - F(x_0)}{h} = f(x_0)$.

    We have $\lim_{h \to 0} \frac{F(x_0 + h) - F(x_0)}{h} = 1/h \int_{x_0} ^{x_0 + h} f(t)dt$. Let $M = \sup_{x \in [x_0, x_0 + h]}$ and $m = \inf_{x \in [x_0, x_0 + h]}$.
    Then certainly $m \leq 1/h \int_{x_0} ^{x_0 + h} f(t)dt \leq M$. 
    Since $f(x)$ is continuous at $x_0$ we have \\
    $\forall 1/q, \; \exists 1/n \sp s.t. \sp \forall x \in [a,b] \; |x - x_0| < 1/n$ we have $|f(x) - f(x_0)| < 1/q$, thus $m, M$ must converge to $f(x_0)$.
    So we have by squeeze theorem \\
    $\lim_{h \to 0} \frac{F(x_0 + h) - F(x_0)}{h} = 1/h \int_{x_0} ^{x_0 + h} f(t)dt = f(x_0)$

    The second part we show that $F'(x_0)$ DNE if $f(x_0)$ is discontinuous. We say that \\$\lim_{x \to x_0^+} f(x) = q$
    and $\lim_{x \to x_0^-} f(x)= r$ where $q \neq r$. We examine $\lim_{h \to 0} \frac{F(x_0 + h) - F(x_0)}{h}$ as we approach from both sides.
    On the left side of zero $\lim_{h \to 0^-}$, $f(x) \to r$, and by the first part $F'(x) \to r$, but on the right side
    of zero: $\lim_{x \to x_0^+}$, $f(x) \to q$, and by the first part $F'(x) \to q$. Since the limit is not the same from both sides
    the limit DNE.
\end{proof}

\end{document}